---
title: Count Regression Model Dominance Analysis
subtitle: Documentation
#author: Joseph Luchman
author: Anonymized for review
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

This notebook provides documentation for the generation of the data used in the manuscript **Relative Importance Analysis for Count Regression Models**.

This document extends on the main manuscript by focusing more closely on implementation details. These implementation details are are not essential for the reader to understand the manuscript but are essential for reproducibility of the results. The details in this notebook also add additional context the manuscript's analyses by, for example, extending the Poisson regression results reported to negative Binomial regression.

Details on the random seed as well as the details of the R environment are available at the end of this notebook.

```{r set-up, include = FALSE}
library(gt)
library(MASS)
library(tidyverse)
library(magrittr)
library(domir)
library(parameters)
library(performance)
library(datawizard)
library(MCMCpack)
library(ggeffects)

set.seed(84490856)
```

# Data Generation

The manuscript describes four tailoring shop characteristic IVs that will be used in the analysis. These IVs are:

  a. equipment reliability or _ER_
  b. assistant staffing levels or _AS_
  c. tailor skill level or _SL_
  d. tailor work experience or _WE_
  
Each of these IVs are generated for the simulated tailoring shops described in the manuscript as the first step in the data generation methodology.

My approach in generating the data for this manuscript was to begin by developing higher-order population parameters that were intended to give a specific set of results from a linear regression. These higher-order population parameters were useful as a conceptual structure from which to generate the data. The data, as generated, were only to be based loosely on this higher-order conceptual structure and the population parameters actually used to generate the data were sampled, and thus varied, from it in a way that was not intended to be directly under my control. As such, the results would in a general sense follow from the higher order conceptual structure imposed on the data but not be completely determined by me. 

This method of developing a well-structured set of parameters from which the observed data's parameters are sampled is advantageous in my view for this manuscript. Specifically, this structure allows the data to be generated in such a way as to illustrate key concepts yet also maintaining an element of randomness and realism in its appearance and in the results they produce.

## Generate IV Data

The generation of the four IVs began with setting up a higher-order population-level covariance matrix describing the variances of and interrelationships between the four tailoring shop IVs. This higher-order variance-covariance matrix was used as a set of parameters from which an sampled variance-covariance was obtained. This sampled variance covariance matrix was used as the population parameters from which the observations from this study were derived.

### Higher-Order Variance-Covariance Structure

The variances of IVs affect their contribution to the $R^2$ and thus will also affect the dominance designations and statistics produced by each IV. As an important determinant of dominance designations and statistics, the IVs were set to different values. The variances chosen were four equally spaced values between standard deviation values of 1 and 2. The first IV, _ER_, had a $\sigma_{ER} = 1.00$ and $\sigma^2_{ER} = 1.00$. The second IV, _AS_, had $\sigma_{AS} = 1.33$ and $\sigma^2_{AS} = 1.78$.  _SL_ had $\sigma_{SL} = 1.67$ and $\sigma^2_{SL} = 2.78$.  Finally, _WE_ had $\sigma_{WE} = 2.00$ and $\sigma^2_{WE} = 4.00$.

Dominance designations and statistics depend on interrelationships between the IVs. I did not have any reason to expect that a specific correlation structure would be more advantageous than another in defining the higher-order structure. As such, I defined the correlation matrix to be "balanced" across IVs such that the total redundancy for any one IV was identical to the others. 

All six correlations between the four IVs were thus designed to take on one of three values .250, .125, and .063 with the following values specified between each of the IVs: $r_{ER,AS} = .250$, $r_{ER,SL} = .125$, $r_{ER,WE} = .063$, $r_{AS,SL} = .063$, $r_{AS,WE} = .125$, and $r_{SL,WE} = .250$.

The code block below sets and reports on the correlation matrix as well as the the variance-covariance matrix on which it is based.

```{r gen-iv-mat}
namelist <- 
  c("ER", "AS", "SL", "WE")

Covariance_Matrix <- 
  c(1, .5^(2:4)*sqrt(1*c((4/3)^2, (5/3)^2, 4))*sqrt(1),
    .5^2*sqrt(1)*sqrt(1*(4/3)^2), (4/3)^2, .5^(4:3)*sqrt(1*(4/3)^2)*sqrt(1*c((5/3)^2, 4)),
    .5^(3:4)*sqrt(1*(5/3)^2)*sqrt(1*c(1, (4/3)^2)), (5/3)^2, .5^2*sqrt(1*(5/3)^2)*sqrt(1*4),
    .5^(4:2)*sqrt(1*4)*sqrt(1*c(1, (4/3)^2, (5/3)^2)), 4) %>%
  matrix(nrow = 4, byrow = TRUE)

Covariance_Matrix %>% 
  as.data.frame() %>%
  set_names(namelist) %>%
  set_rownames(namelist) %>%
  gt(rownames_to_stub = TRUE) %>%
  tab_header("Table S1: Higher-order Population Covariance Matrix") %>%
  fmt_number(columns = 2:5, decimals = 4)

Covariance_Matrix %>% cov2cor() %>% 
  as.data.frame() %>%
  set_names(namelist) %>%  
  set_rownames(namelist) %>%
  gt(rownames_to_stub = TRUE) %>%
  tab_header("Table S2:  Higher-order Population Correlation Matrix")
```

### Sampled Population Parameter Values

The population parameters that were used to generate observations were based on the higher order variance-covariance matrix in that it was used as the scale parameter in an inverse Wishart distribution. The degree of freedom parameter for the inverse Wishart distribution was set to a large value, in this case 100. The large value for the degrees of freedom was chosen as it has the effect of reducing the variances of the sampled matrix which stabilizes the correlations of the values sampled to be closer to the population values. 

A single draw was taken from the inverse Wishart and the values obtained were used as the population parameters for the simulated data.

The code block below takes the variance-covariance matrix sample and reports on the sampled values as well as the correlation matrix of the sampled values.

```{r sample-iv-mat}
Covariance_Matrix_Use <- 
  riwish(100, Covariance_Matrix)

Covariance_Matrix_Use %>% 
  as.data.frame() %>%
  set_names(namelist) %>%
  set_rownames(namelist) %>%
  gt(rownames_to_stub = TRUE) %>%
  tab_header("Table S3: Sampled Population Covariance Matrix") %>%
  fmt_number(columns = 2:5, decimals = 4)

Covariance_Matrix_Use %>% cov2cor() %>% 
  as.data.frame() %>%
  set_names(namelist) %>%  
  set_rownames(namelist) %>%
  gt(rownames_to_stub = TRUE) %>%
  tab_header("Table S4: Sampled Population Correlation Matrix") %>%
  fmt_number(columns = 2:5, decimals = 4)
```

Note that the sampled variance-covariance matrix has variance values that are around $1/100$ of the values of the original matrix due to the degrees of freedom from the inverse Wishart. The variances of all the variables will be corrected but the correction will be applied later when the data are generated.

Although the variances of the variables reported on in Table S3 are too small, the sampled correlations in Table S4 appear reasonable and within expectation for organizational science data. Thus, the goal of sampling the population parameter values to be used to generate the analysis data from an inverse Wishart was successful.

### Generate Obseved Data

The four tailoring shop characteristic IVs were generated in a series of random draws from a Multivariate Normal distribution using the sampled population parameters each with a mean of 0.

The number of draws from the Multivariate Normal distribution or the size of tailoring shop sample was also determined through a random process. The value used was taken from a single draw from a random uniform distribution that had a value falling between 5,000 and 10,000 rounded to the nearest integer. The range that was chosen should allow for stable estimates from these data yet be within a range observed of many large social surveys.

The code block below samples the sample size value and takes all IV samples. The block also reports on descriptive statistics from the sampled IV observations including the sample size.

```{r gen-iv-data, message=FALSE}
total_n <- 
  runif(n = 1, min = 5000, max = 10000) %>% 
  round()

Data_Frame <- 
  mvrnorm(n = total_n, 
          mu = rep(0, times = 4), 
          Sigma = Covariance_Matrix_Use) %>% 
  as.data.frame() %>%
  multiply_by(10) %>%
  set_names(namelist)

Data_Frame %>%
  summarise(
    across(everything(), .fns = mean),
    ) %>% 
  pivot_longer(everything(), names_to = "IV Name", values_to = "Mean") %>%
  left_join(
  Data_Frame %>%
  summarise(
    across(everything(), .fns = sd),
    ) %>% pivot_longer(everything(), names_to = "IV Name", 
                       values_to = "Standard Deviation")
  ) %>%
  left_join(
    Data_Frame %>% 
      cor %>% 
      as_tibble(rownames = "IV Name")
  ) %>%
  gt(rowname_col = "IV Name") %>%
  tab_header("Table S5: Sampled Data Descriptive Statistics") %>%
  fmt_number(columns = 2:7, decimals = 4) %>%
  tab_spanner(columns = c(ER, AS, SL, WE), label = "Correlations") %>%
  tab_style(
    style = cell_borders(sides = "right"),
    locations = cells_body(columns = "Standard Deviation")
  ) %>%
  tab_source_note(str_c("Sample Size of Simulated Data is ", 
                        nrow(Data_Frame) %>% format(big.mark = ","), "."))
```

Note the correction of the variances/standard deviations in the table above. The all IV values were multiplied by 10 to be closer to the original, higher-order population range.

## Generate Dependent Variables

The methods used to develop each DV in the sections below were devised to ensure a specific relationship form and strength with each IV. The methodology also ensured a specific distribution type for the specific DV as was required for the data analytic demonstrations in this manuscript. 

This section creates multiple count DVs from a single Normally distributed DV. The intuition behind using this approach is that a Normally distributed variable is straightforward to work with. The researcher can determine the values of regression coefficients with IVs and how those coefficients translate into variance explained directly with Normally distributed variables that can be later translated into the desired count distributional form. 

Translating the Normally distributed DV into each different count DV uses each variable's underlying probability distribution as the shared metric into which one distribution can be translated into another. For example, consider translating a Normally distributed value of 4, assuming a mean of 1 and standard deviation of 1.5, into the most likely value in a Poisson distribution with a mean of 5. The cumulative probability of observing a value of 4 given mean of 1 and standard deviation of 1.5 is about `r pnorm(4, 1, 1.5) |> round(5)`. The best value to translate into in the Poisson distribution with a mean of 5 would then be the nearest integer value in the Poisson distribution that corresponds with a cumulative probability of `r pnorm(4, 1, 1.5) |> round(5)`. The integer 9 has a cumulative probability of `r ppois(9, 5) |> round(5)` (an absolute difference of `r (ppois(9, 5) - pnorm(4, 1, 1.5)) |> round(5) |> abs()`) and the integer 10 has a cumulative probability of `r ppois(10, 5) |> round(5)` (an absolute difference of `r (ppois(10, 5) - pnorm(4, 1, 1.5)) |> round(5) |> abs()`). Thus, the most likely value to translate into would be 10. This is the approach taken below when translating the underlying Normally distributed variable into a Poisson and negative Binomial distributed counterpart.

The advantage of the cumulative probability and quantile function (i.e., the name of the function to back translate a cumulative probability into an observed DV value) translation approach is that it preserves relationships and predictive utility established with Normally distributed variable, but ensures the characteristics of the DV fit expectations (i.e., the DV is comprised of non-negative integers with a specific mean).

### Generate Underlying Normally Distributed Dependent Variable

The generation of the underlying Normally distributed variable extended from the methodology that was established above where a set of higher-order population parameters are first set and adjusted from using a draws from a specific distribution to reduce the effect of my decisions on the results.

Conceptually, the underlying Normally distributed variable can be thought of as a latent propensity each tailoring shop has for making more garments. This garment propensity variable (called $GP$) is generated as a linear combination of the four tailoring shop IVs. In devising the higher-order population coefficients, I thought it would be convenient to generate coefficients that, when combined with the higher-order population variances, would produce a specific $R^2$ under idealized conditions. In generating these coefficients, I intentionally ignored the higher-order population covariances to allow this section to be easier to follow and because I was not so much trying to attain a specific $R^2$ in the observed data but rather to have a reasonable, systematic approach to generating IV coefficient values.
	
#### Higher-Order Population Parameters

The approach used to generate the higher-order IV coefficients values was to devise values such that the coefficients achieve a value of $R^2 = .12$. I also wanted to assign the coefficient values in a way such that no one IV contributed more to the value than any other. The simplest way to do so was to ignore the IV covariances and use the $R^2 = \sum\beta^2\sigma^2$ formula for computing the $R^2$ to work backward to obtain a value that ascribes each IV a contribution of .04. The values chosen were then: $\beta_{ER} =.20$,  $\beta_{AS} =.15$,  $\beta_{SL} =.12$, $\beta_{WE} =.10$.

The code block below sets the higher order IV coefficient population parameters and reports on their values.

```{r pop-coefs}
Coefficient_Vector <- 
  c(.2, sqrt(.04/(4/3)^2), sqrt(.04/(5/3)^2), .1)

Coefficient_Vector %>%
  data.frame(name = namelist, value = .) %>%
  pivot_wider(id_cols = everything()) %>%
  gt() %>%
  tab_header("Table S6: Higher-order Population Coefficient Values") %>%
  fmt_number(columns = 1:4, decimals = 4)
```

#### Sampled Population Parameters

The higher-order population values were used as the means in four draws from a Normal distribution each with a standard deviation of .05. As the coefficients were all within a relatively narrow range, the standard deviation of .05 allowed for the possibility that, by chance, the rank ordering of coefficient magnitudes could change. 

The code block below implements the sampling of the coefficient values and reports on their values.

```{r sampled-coeff}
Coefficient_Vector_Use <- 
  rnorm(4, Coefficient_Vector, .05)

names(Coefficient_Vector_Use) <- namelist

Coefficient_Vector_Use %>%
  data.frame(name = namelist, value = .) %>%
  pivot_wider(id_cols = everything()) %>%
  gt() %>%
  tab_header("Table S7: Sampled Population Coefficient Values") %>%
  fmt_number(columns = 1:4, decimals = 4)
```

The sampled population coefficients varied from the higher-order values and varied from the higher-order coefficients' rank order as $\beta_{WE} > \beta_{SL}$ in the sampled values whereas the reverse was true of the higher-order values.

#### Generate Observed Values

The garment propensity variable $GP$ was generated as a linear combination of the four tailoring shop characteristics and their respective coefficients. The error variance for $GP$ was set to be $1 - \sigma^2_{ER\beta_{ER} + AS\beta_{AS} + SL\beta_{SL} + WE\beta_{WE}}$ thus forcing the variance of $GP$ to be 1. The mean of $GP$ is also set to be 0.

The code block below generates and reports on the descriptive statistics of $GP$.

```{r gen-y-normal}
Data_Frame %<>%
  mutate(
    GP = 
      ER*Coefficient_Vector_Use[["ER"]] + AS*Coefficient_Vector_Use[["AS"]] + 
      SL*Coefficient_Vector_Use[["SL"]] + WE*Coefficient_Vector_Use[["WE"]], 
    GP = GP + rnorm(total_n, 0, sqrt(1 - var(GP)))
  )

Data_Frame %>%
  summarise("Mean" = mean(GP)) %>% 
  bind_cols(
    Data_Frame %>%
      summarise("Standard Deviation" = sd(GP))
  ) %>%
  bind_cols(
    Data_Frame %>% 
      cor %>% 
      as_tibble(rownames = "IV Name") %>%
      filter(`IV Name` == "GP") %>%
      select(-GP, -`IV Name`)
  ) %>%
  gt() %>%
  tab_header("Table S8: Underlying Normal Dependent Variable Descriptive Statistics") %>%
  fmt_number(columns = 1:6, decimals = 4) %>%
  tab_spanner(columns = c(ER, AS, SL, WE), label = "Correlations") %>%
  tab_style(
    style = cell_borders(sides = "right"),
    locations = cells_body(columns = "Standard Deviation")
  )
```

In addition, a histogram of $GP$ is reported.

```{r y-gph, message=FALSE}
Data_Frame %>%
  select(GP) %>%
  ggplot(aes(x = GP)) +
  stat_bin() +
  ggtitle("Figure Sa: Distribution of the Underlying Normal Dependent Variable") +
  theme_light()
```

Finally, a regression predicting $GP$ using the four tailoring shop IVs is estimated and reported on below to confirm that the sampled population coefficient values are re-obtainable in the data.

```{r y-regress}
lm(GP ~ ., data = Data_Frame) %>% 
  parameters() %>%
  select(-df_error, -CI) %>%
  rename(Low = "CI_low", High = "CI_high") %>%
  gt(rowname_col = "Parameter") %>%
  fmt_number(columns = 2:7, decimals = 4) %>%
  tab_spanner(columns = c(Low, High), label = "Confidence Interval") %>%
  tab_header("Table S9: Underlying Normal Dependent Variable Linear Regression")
```

The results confirm that the coefficients are recoverable in the data.

### Generate Poisson Dependent Variable

The Poisson distributed variable related to the number of sport jackets produced (i.e., $SJ$) was based on the garment propensity variable and translated to the Poisson distribution using the cumulative propensity to quantile method described above.

$SJ$ was given a mean of 1 was chosen to make the $SJ$ results as close to those from $GP$ as possible; using this approach both DVs will have variances of 1.	

The code block below implements the translation process and reports on the descriptive results.

```{r gen-y-poisson}
Data_Frame %<>%
  mutate(
    SJ = GP %>% pnorm(log.p = TRUE) %>% qpois(1, log.p = TRUE)
  )

Data_Frame %>%
  summarise("Mean" = mean(SJ)) %>% 
  bind_cols(
    Data_Frame %>%
      summarise("Standard Deviation" = sd(SJ))
  ) %>%
  bind_cols(
    Data_Frame %>% 
      cor %>% 
      as_tibble(rownames = "IV Name") %>%
      filter(`IV Name` == "SJ") %>%
      select(-SJ, -GP, -`IV Name`)
  ) %>%
  gt() %>%
  tab_header("Table S10: Poisson Dependent Variable Descriptive Statistics") %>%
  fmt_number(columns = 1:6, decimals = 4) %>%
  tab_spanner(columns = c(ER, AS, SL, WE), label = "Correlations") %>%
  tab_style(
    style = cell_borders(sides = "right"),
    locations = cells_body(columns = "Standard Deviation")
  )
```

In addition, a histogram of $SJ$ is provided below.

```{r pois-gph, message=FALSE}
Data_Frame %>%
  select(SJ) %>%
  ggplot(aes(x = SJ)) +
  stat_count() +
  ggtitle("Figure Sb: Distribution of the Poisson Dependent Variable") +
  theme_light()
```

### Generate Negative Binomial Dependent Variable

The negative Binomial distributed variable related to the number of overcoats produced (i.e., $OC$) was also based on the garment propensity variable translated to the negative Binomial distribution using the cumulative propensity to quantile method.

The generation of the $OC$ also sought to ensure as much similarity to the $GP$ variable as possible while also requiring that $OC$'s distribution fail to meet the assumptions of the Poisson distribution. The quantile function values that $GP$ was translated into were then a _size_ parameter of .5 and _mu_ parameter of 1.

This combination of _size_ and _mu_ parameters result in a mean (i.e., the _mu_/$\mu$ value) of 1 but a variance that substantially exceeded 1; in this case  or a value of 3 as $\sigma^{2} = \mu + \frac{\mu^2}{size}$.

The code block below implements the translation process and reports on the descriptive results.

```{r gen-y-neg-bin}
Data_Frame %<>%
  mutate(
    OC = GP %>% pnorm(log.p = TRUE) %>% qnbinom(size = .5, mu = 1, log.p = TRUE)
  )

Data_Frame %>%
  summarise("Mean" = mean(OC)) %>% 
  bind_cols(
    Data_Frame %>%
      summarise("Standard Deviation" = sd(OC))
  ) %>%
  bind_cols(
    Data_Frame %>% 
      cor %>% 
      as_tibble(rownames = "IV Name") %>%
      filter(`IV Name` == "OC") %>%
      select(-SJ, -GP, -`IV Name`, -OC)
  ) %>%
  gt() %>%
  tab_header("Table S11: Negative Binomial Dependent Variable Descriptive Statistics") %>%
  fmt_number(columns = 1:6, decimals = 4) %>%
  tab_spanner(columns = c(ER, AS, SL, WE), label = "Correlations") %>%
  tab_style(
    style = cell_borders(sides = "right"),
    locations = cells_body(columns = "Standard Deviation")
  )
```

In addition, a histogram of $OC$ is provided below.

```{r neg-bin-gph, message=FALSE}
Data_Frame %>%
  select(OC) %>%
  ggplot(aes(x = OC)) +
  stat_count() +
  ggtitle("Figure Sc: Distribution of the Negative Binomial Dependent Variable") +
  theme_light()
```

## Report Primary Generated Data Descriptives

This section produces Table 4 in the manuscript including the descriptive statistics for all four IVs and the $SJ$ DV reported on in the manuscript.

```{r display-observed-descriptives}
Data_Frame %>%
  summarise(across(everything(), mean)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Mean") %>%
  left_join(
    Data_Frame %>%
      summarise(across(everything(), sd)) %>%
      pivot_longer(everything(), names_to = "Variable", 
                   values_to = "Standard Deviation"),
    by = "Variable"
  ) %>%
  left_join(
    Data_Frame %>% 
      cor %>% 
      as_tibble(rownames = "Variable"),
    by = "Variable"
  ) %>%
  filter(!(Variable %in% c("GP", "OC"))) %>%
  select(-GP, -OC) %>%
  gt() %>%
  tab_header("Table 4: Descriptive Statistics") %>%
  fmt_number(columns = 2:8, decimals = 4) %>%
  tab_spanner(columns = c(ER, AS, SL, WE, SJ), label = "Correlations") %>%
  tab_style(
    style = cell_borders(sides = "right"),
    locations = cells_body(columns = "Standard Deviation")
  ) %T>%
  print %>%
  gtsave(filename = "descrips_initial.tex", path = "./includes/")
```

## Generate Differential Exposure Contaminated Dependent Variables

The two differential exposure contaminated variables, sport jacket production during religious holidays ($SJ_{RH}$) and sport jacked production during voluntary holidays ($SJ_{VH}$) were generated in a way similar to that of the Poisson and negative Binomial variables above.

### Random Differential Exposure

The $SJ_{RH}$ DV was generated from the $GP$ variable like $SJ$ above but was based on repeated Binomial trials as opposed to the Poisson distribution directly. As is discussed in the manuscript, repeated trials from a binomial distribution are known to be Poisson distributed with a rate/mean parameter that can be derived as $np = \lambda$ where In this case the $n$ is the number of trials and $p$ is the probability of the event occurring.

The number of Binomial trials are then used as the metric determining each observation's differential exposure to the probability or the count generating process. These number of Binomial trials representing number of days working during the two week period with religious holidays ($RH$) were based on a random draw from a uniform distribution for each observation adhering to the constraint that the value for each observation was an integer ranging from 1 to 10 working days.

The probability value chosen for the Binomial distribution was .1. This value was chosen as it is the value that would obtain the mean of $SJ$ given identical exposure for all tailoring shops assuming they worked each working day (i.e., $10*.1 = 1$).

The code block below generates both $RH$ and $SJ_{RH}$. Descriptive statistics for both are reported.

```{r diff-exp-rnd-gen}
Data_Frame %<>%
  mutate(
    RH = sample(1:10, total_n, replace = TRUE),
    SJ_RH = 
      GP %>% pnorm(log.p = TRUE) %>%
      qbinom(RH, .1, log.p = TRUE)
  )

Data_Frame %>%
  summarise(across(c(SJ_RH, RH), mean)) %>% 
  pivot_longer(everything(), 
               names_to = "Variable", values_to = "Mean") %>% 
  left_join(
    Data_Frame %>%
      summarise(across(c(SJ_RH, RH), sd)) %>% 
      pivot_longer(everything(), 
                   names_to = "Variable", values_to = "Standard Deviation"),
    by = "Variable"
  ) %>%
  left_join(
    Data_Frame %>% 
      cor %>% 
      as_tibble(rownames = "Variable") %>%
      filter(Variable %in% c("SJ_RH", "RH")) %>%
      select(ER, AS, SL, WE, Variable),
    by = "Variable"
  ) %>%
  gt() %>%
  tab_header("Table S12: Random Differential Exposure Poisson Dependent Variable Descriptive Statistics") %>%
  fmt_number(columns = 2:7, decimals = 4) %>%
  tab_spanner(columns = c(ER, AS, SL, WE), label = "Correlations") %>%
  tab_style(
    style = cell_borders(sides = "right"),
    locations = cells_body(columns = "Standard Deviation")
  )
```

A graph of the random differential exposure variable is reported below.

```{r rnd-exps-gph}
Data_Frame %>%
  select(RH) %>%
  mutate(RH = as_factor(RH)) %>%
  ggplot(aes(x = RH)) +
  stat_count() +
  ggtitle("Figure Sd: Distribution of the Random Differential Exposure Variable") +
  theme_light()
```

In addition, a graphic depicting the random differential exposure contaminated Poisson distributed variable is depicted.

```{r diff-exp-rnd-gph}
Data_Frame %>%
  select(SJ_RH) %>%
  ggplot(aes(x = SJ_RH)) +
  stat_count() +
  ggtitle("Figure Se: Distribution of the Random Differential Exposure\nPoisson Dependent Variable") +
  theme_light()
```

Finally, a graphic that depicts the differential exposure contaminated DV across levels of differential exposure.

```{r diff-exp-rnd-xtab}
Data_Frame %>%
  select(SJ_RH, RH) %>%
  ggplot(aes(x = SJ_RH)) +
  stat_count() +
  ggtitle("Figure Sf: Distribution of the Random Differential Exposure\nPoisson Dependent Variable Across Levels of Differential Exposure") +
  theme_light() + 
  facet_wrap(vars(RH), nrow = 2)
```

### Correlated Differential Exposure Depedent Variable

The $SJ_{VH}$ DV, like $SJ_{RH}$, was generated from the $GP$ variable as based on repeated Binomial trials. $SJ_{VH}$ differed from $SJ_{RH}$ only in how the differential exposure variable was constructed.

$SJ_{VH}$'s differential exposure variable was generated in a manner more similar to $GP$ itself. In fact, the number of Binomial trials representing number of days working during the two week period with voluntary holidays ($VH$) used the higher-order population coefficient values used to generate $GP$ but multiplied by -1. The -1 transformed higher-order population coefficient values are then used as the means of four draws from a Normal distribution each with a standard deviation of .05 following the approach applied to obtaining the sampled population coefficient values for $GP$.

The code block below implements the sampling and reports the sampled population coefficient values that will be used for $VH$.

```{r diff-exp-corr-coef}
Coefficient_Vector_Diff_Exp <- 
  rnorm(4, Coefficient_Vector*-1, .05)

names(Coefficient_Vector_Diff_Exp) <- namelist

Coefficient_Vector_Diff_Exp %>%
  data.frame(name = namelist, value = .) %>%
  pivot_wider(id_cols = everything()) %>%
  gt() %>%
  tab_header("Table S13: Sampled Population Coefficient Values for Differential Exposure") %>%
  fmt_number(columns = 1:4, decimals = 4)
```

A Normally distributed initial $VH$ value is constructed in the same way as $GP$ above and is translated into a Uniform distributed variable ranging from 0 to 10. These uniform distributed values are not integer valued and are coerced to integers. 

The Uniform, integer-valued $VH$ is then used in the same way as $RH$ above as a differential exposure factor for the Binomial trials.

The code block below generates $VH$ and $SJ_{VH}$ and reports on descriptives.

```{r diff-exp-corr-gen}
Data_Frame %<>%
  mutate(
    VH =
      ER*Coefficient_Vector_Diff_Exp[["ER"]] + AS*Coefficient_Vector_Diff_Exp[["AS"]] + 
      SL*Coefficient_Vector_Diff_Exp[["SL"]] + WE*Coefficient_Vector_Diff_Exp[["WE"]],
    VH = VH + rnorm(total_n, 0, sqrt(1 - var(VH))),
    VH = VH %>% pnorm(log.p = TRUE) %>% 
      qunif(0, 10, log.p = TRUE) %>% ceiling(),
    SJ_VH = GP %>% pnorm(log.p = TRUE) %>% 
      qbinom(VH, .1, log.p = TRUE)
  )

Data_Frame %>%
  summarise(across(c(SJ_VH, VH), mean)) %>% 
  pivot_longer(everything(), 
               names_to = "Variable", values_to = "Mean") %>% 
  left_join(
    Data_Frame %>%
      summarise(across(c(SJ_VH, VH), sd)) %>% 
      pivot_longer(everything(), 
                   names_to = "Variable", values_to = "Standard Deviation"),
    by = "Variable"
  ) %>%
  left_join(
    Data_Frame %>% 
      cor %>% 
      as_tibble(rownames = "Variable") %>%
      filter(Variable %in% c("SJ_VH", "VH")) %>%
      select(ER, AS, SL, WE, Variable),
    by = "Variable"
  ) %>%
  gt() %>%
  tab_header("Table S14: Correlated Differential Exposure Poisson Dependent Variable Descriptive Statistics") %>%
  fmt_number(columns = 2:7, decimals = 4) %>%
  tab_spanner(columns = c(ER, AS, SL, WE), label = "Correlations") %>%
  tab_style(
    style = cell_borders(sides = "right"),
    locations = cells_body(columns = "Standard Deviation")
  )
```

Below a graph of the correlated differential exposure variable is provided.

```{r corr-exps-gph}
Data_Frame %>%
  select(VH) %>%
  mutate(VH = as_factor(VH)) %>%
  ggplot(aes(x = VH)) +
  stat_count() +
  ggtitle("Figure Sg: Distribution of the Correlated Differential Exposure Variable") +
  theme_light()
```

In addition, a graphic depicting the correlated differential exposure contaminated Poisson distributed variable is depicted.

```{r diff-exp-corr-gph}
Data_Frame %>%
  select(SJ_VH) %>%
  ggplot(aes(x = SJ_VH)) +
  stat_count() +
  ggtitle("Figure Sh: Distribution of the Correlated Differential Exposure\nPoisson Dependent Variable") +
  theme_light()
```

Finally, a graphic that depicts the differential exposure contaminated DV across levels of differential exposure.

```{r diff-exp-corr-xtab}
Data_Frame %>%
  select(SJ_VH, VH) %>%
  ggplot(aes(x = SJ_VH)) +
  stat_count() +
  ggtitle("Figure Si: Distribution of the Correlated Differential Exposure\nPoisson Dependent Variable Across Levels of Differential Exposure") +
  theme_light() + 
  facet_wrap(vars(VH), nrow = 2)
```

## Report Differential Exposure Contaminated Data Descriptives

This section produces Table 8 in the manuscript including the descriptive statistics for both new DVs and their correlations with the IVs.

```{r display-exposure-descriptives}
Data_Frame %>%
  summarise(across(c(SJ_RH, SJ_VH), mean)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Mean") %>%
  left_join(
    Data_Frame %>%
      summarise(across(c(SJ_RH, SJ_VH), sd)) %>%
      pivot_longer(everything(), names_to = "Variable", 
                   values_to = "Standard Deviation"),
    by = "Variable"
  ) %>%
  left_join(
    Data_Frame %>% 
      cor %>% 
      as_tibble(rownames = "Variable"),
    by = "Variable"
  ) %>%
  filter(Variable %in% c("SJ_RH", "SJ_VH")) %>%
  select(Variable, Mean, `Standard Deviation`, ER, AS, SL, WE) %>%
  gt() %>%
  tab_header("Table 8: Descriptive Statistics with Differential Exposure") %>%
  fmt_number(columns = 2:7, decimals = 4) %>%
  tab_spanner(columns = c(ER, AS, SL, WE), label = "Correlations") %>%
  tab_style(
    style = cell_borders(sides = "right"),
    locations = cells_body(columns = "Standard Deviation")
  ) %T>%
  print %>%
  gtsave(filename = "descrips_exposure.tex", path = "./includes/")
```

```{r save-data, results='hide', include=FALSE}
saveRDS(Data_Frame, "./Data_Results/DF.rds")
```

```{r load-data, results='hide', include=FALSE}
Data_Frame <- 
  readRDS("./Data_Results/DF.rds")
```

# Primary Modeling

This section describes the model estimation and dominance analysis of the primary analysis models involving the primary $SJ$ and the unreported $OC$ DVs.

## Modeling Sport Jacket Production

All modeling and reporting of $SJ$ is implemented in this section.

### Obtain Modeling Results

The code block below estimates, formats, and reports on the Poisson regression with $SJ$. 

These results form Table 5 of the manuscript.

```{r SJ-pois-reg}
SJ_pois_reg <- 
  glm(SJ ~ ER + AS + SL + WE, 
      data = Data_Frame, 
      family = poisson()) 

SJ_pois_param <- 
  SJ_pois_reg %>% 
  parameters() 

SJ_pois_param  %>% 
  select(-df_error, -CI, -z, -p) %>%
  {bind_rows(slice_tail(., n = 4), slice_head(., n = 1))} %>%
  rename(Low = "CI_low", High = "CI_high", B = "Coefficient", `\\sigma_{B}` = "SE") %>%
  mutate(`e^B` = exp(B), 
         Parameter = str_replace(Parameter, "\\(Intercept\\)", "Intercept")) %>%
  gt(rowname_col = "Parameter") %>%
  fmt_number(columns = 2:6, decimals = 4) %>%
  tab_spanner(columns = c(Low, High), label = "95% Confidence Interval") %>%
  tab_header("Table 5: Poisson Regression Predicting Sport Jackets Produced") %T>%
  print %>%
  gtsave(filename = "poisson_coeff.tex", path = "./includes/")
```

Below the marginal effects from the $SJ$ model are depicted in a graphic.

```{r SJ-pois-mgn}
map(c("ER", "AS", "SL", "WE"),
    \(iv) {
      
      lst <- 
        list(-2:2) %>%
        set_names(iv)
      
      SJ_pois_reg %>%
        emmeans::emmeans(reformulate(iv), 
                         at = lst) %>%
        as_tibble %>%
        rename(mgn = all_of(iv)) %>%
        mutate(var = iv %>% as_factor,
               emmean = exp(emmean))
    }
) %>%
  list_rbind() %>%
  ggplot(aes(x = mgn, y = emmean, group = var, color = var)) + 
  geom_line() + scale_color_viridis_d() + theme_light() + 
  ylab("Predicted Counts") + xlab("Values of Tailoring Characteristic") + 
  labs(color = "Tailoring\nCharacteristic") + 
  ggtitle("Figure Sj: Marginal Effects of the Sport Jacket\nProduction Model")
```

### Obtain All Submodels' R-squares

The code block below captures all sub-model $R^2_{DEV}$ values. The values obtained in this section form Table 6 in the manuscript.

```{r SJ-pois-reg-subsets}
IV_subsets <- 
  expand_grid(c("ER", ""), c("AS", ""), c("SL", ""), c("WE", "")) %>%
  set_names(c("ER", "AS", "SL", "WE")) %>%
  mutate(num_per = rowSums(across(everything(), .fns = ~ str_length(.) > 1))) %>%
  arrange(num_per, desc(ER), desc(AS), desc(SL), desc(WE)) %>%
  select(-num_per) %>%
  slice(-1) %>% 
  t() %>%
  as_tibble() 

SJ_pois_subsets <-
  map_dbl(IV_subsets,
          \(ivs) {
            discard(ivs, ~ str_length(.) < 2) %>%
            reformulate(response = "SJ") %>%
              glm(data = Data_Frame, family = poisson()) %>%
              r2_kullback(adjust = FALSE)
          }
  )

IV_subset_names <-
  map_chr(IV_subsets, 
          \(ivs) {
            discard(ivs, ~ str_length(.) < 2) %>%
            str_c(., collapse = " + ")
          }
  )

IV_subset_names %>% 
  str_c("SJ ~ ", .) %>%
  as_tibble() %>%
  bind_cols(SJ_pois_subsets) %>%
  gt() %>%
  tab_header("Table 6: R^2_{DEV} by Sub-model") %>%
  fmt_number(columns = 2, decimals = 4) %>%
  cols_label(everything() ~ "") %T>%
  print() %>%
  gtsave(filename = "all_subsets.tex", path = "./includes/")
```

### Dominance Analytic Results

The code block below implements the dominance analysis using $SJ$.

```{r SJ-pois-DA}
SJ_pois_DA <-
  domir(SJ ~ ER + AS + SL + WE, 
        \(fml, ...) {
          res <- 
            glm(fml, ...) 
          return(r2_kullback(res, adjust = FALSE))
        },
        data = Data_Frame, family = poisson())

SJ_pois_DA %>% 
  pluck("General_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  left_join(SJ_pois_DA %>% 
              pluck("Standardized") %>%
              as_tibble(rownames = "Variable"),
            by = "Variable") %>%
  set_names(c("Variable", "General Dominance", "Standardized")) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S15: Poisson Model General Dominance Statistics") %>%
  fmt_number(columns = 2:3, decimals = 4) %>%
  tab_source_note(str_c("Overall Deviance R-square is ", 
                        SJ_pois_reg %>% r2_kullback() %>% 
                          sprintf("%5.4f", .), "."))

SJ_pois_DA %>% 
  pluck("Conditional_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  set_names(c("Variable", str_c("Subset Size: ", 1:4))) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S16: Poisson Model Conditional Dominance Statistics") %>%
  fmt_number(columns = 2:5, decimals = 4)

SJ_pois_DA %>% 
  pluck("Complete_Dominance") %>%
  as_tibble(rownames = "Dominating Variable") %>%
  mutate(
    `Dominating Variable` = str_remove(`Dominating Variable`, "Dmnates_")
  ) %>%
  set_names(c("Dominating Variable", str_c("Dominated Variable: ", 
                                           c("ER", "AS", "SL", "WE")))) %>%
  gt(rowname_col = "Dominating Variable") %>%
  tab_header("Table S17: Poisson Model Complete Dominance Designations") %>%
  sub_missing() %>% 
  tab_stubhead("Dominating Variable")
```

The code block below reports Table 7 in the manuscript.

```{r gend-dom-display}
SJ_pois_DA %>% 
  pluck("General_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table 7: General Dominance Statistics") %>%
  cols_label(everything() ~ "") %>%
  fmt_number(columns = 2, decimals = 4) %T>%
  print %>%
  gtsave(filename = "gen_dom.tex", path = "./includes/")
```

The Figure 1 in the manuscript is also produced below.

```{r condit-domin-display, fig.height = 3, fig.width = 4.5}
SJ_pois_DA %>%
  pluck("Conditional_Dominance") %>%
  as_tibble(rownames = "IV") %>%
  pivot_longer(
    cols = starts_with("subset_size"),
    names_to = "Subset Size",
    values_to = "Conditional Dominance Statistic",
    names_prefix = "subset_size_"
    ) %>% 
  mutate(
    IV = fct_relevel(IV, "ER", "AS", "SL", "WE"),
    `Subset Size` = `Subset Size` %>% as.integer
  ) %>%
  ggplot(
    aes(x = `Subset Size`, y = `Conditional Dominance Statistic`, group = IV, color = IV)
  ) + geom_line() + 
  theme_linedraw() +
  labs(linetype = "") + 
  coord_trans(xlim = c(.9, 4.1), ylim = c(.015, .185), expand = FALSE, y = "log") + 
  theme(legend.position = c(.90, .89), legend.box.background = element_rect(color = "black"), 
        legend.title = element_blank(), legend.text = element_text(size = 7), 
        legend.key.height = unit(7, "pt"), axis.text.y = element_text(size = 7), 
        legend.margin = margin(b = .5, l = .5, r = .5),
        axis.title = element_text(family = "serif")) + 
  scale_y_continuous(n.breaks = 5) + scale_color_viridis_d()

ggsave("condit_gph.png", height = 4*.75, width = 6*.75, 
       units = "in", path = "./includes/")
```

## Modeling Sport Jacket Production

All modeling and reporting of $OC$ is implemented in this section.

Ultimately, these results were not included in the manuscript as they did not meaningfully extend on the Poisson regression results.

### Obtain Modeling Results

The code block below estimates, formats, and reports on the negative Binomial regression with $OC$. The Theta parameter is included in a footnote.

```{r OC-nb-reg}
OC_nb_reg <- 
  glm.nb(OC ~ ER + AS + SL + WE, 
      data = Data_Frame) 

OC_nb_param <- 
  OC_nb_reg %>% 
  parameters() 

OC_nb_param  %>% 
  select(-df_error, -CI, -z, -p) %>%
  {bind_rows(slice_tail(., n = 4), slice_head(., n = 1))} %>%
  rename(Low = "CI_low", High = "CI_high", B = "Coefficient") %>%
  mutate(`e^B` = exp(B), 
         Parameter = str_replace(Parameter, "\\(Intercept\\)", "Intercept")) %>%
  gt(rowname_col = "Parameter") %>%
  fmt_number(columns = 2:6, decimals = 4) %>%
  tab_spanner(columns = c(Low, High), label = "95% Confidence Interval") %>%
  tab_header("Table S18: Negative Binomial Regression") %>% 
  tab_source_note(str_c("Theta parameter is ", 
                        OC_nb_reg$theta %>% 
                          format(big.mark = ",", digits = 4), "."))
```

Below the marginal effects from the $OC$ model are depicted in a graphic.

```{r OC-nv-mgn}
map(c("ER", "AS", "SL", "WE"),
    \(iv) {
      
      lst <- 
        list(-2:2) %>%
        set_names(iv)
      
      OC_nb_reg %>%
        emmeans::emmeans(reformulate(iv), 
                         at = lst) %>%
        as_tibble %>%
        rename(mgn = iv) %>%
        mutate(var = iv %>% as_factor,
               emmean = exp(emmean))
    }
) %>%
  list_rbind() %>%
  ggplot(aes(x = mgn, y = emmean, group = var, color = var)) + 
  geom_line() + scale_color_viridis_d() + theme_light() + 
  ylab("Predicted Counts") + xlab("Values of Tailoring Characteristic") + 
  labs(color = "Tailoring\nCharacteristic") + 
  ggtitle("Figure Sk: Marginal Effects of the Overcoat\nProduction Model")
```

### Dominance Analytic Results

The code block below implements the dominance analysis using $OC$.

```{r OC-nb-DA}
OC_nb_DA <-
  domir(OC ~ ER + AS + SL + WE, 
        \(fml, ...) {
          res <- 
            glm.nb(fml, ...) 
          return(r2_kullback(res, adjust = FALSE))
        },
        data = Data_Frame)

OC_nb_DA %>% 
  pluck("General_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  left_join(OC_nb_DA %>% 
              pluck("Standardized") %>%
              as_tibble(rownames = "Variable"),
            by = "Variable") %>%
  set_names(c("Variable", "General Dominance", "Standardized")) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S19: Negative Binomial Model General Dominance Statistics") %>%
  fmt_number(columns = 2:3, decimals = 4) %>%
  tab_source_note(str_c("Overall Deviance R-square is ", 
                        OC_nb_reg %>% r2_kullback(adjust = FALSE) %>% 
                          sprintf("%5.4f", .), "."))

OC_nb_DA %>% 
  pluck("Conditional_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  set_names(c("Variable", str_c("Subset Size: ", 1:4))) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S20: Negative Binomial Model Conditional Dominance Statistics") %>%
  fmt_number(columns = 2:5, decimals = 4)

OC_nb_DA %>% 
  pluck("Complete_Dominance") %>%
  as_tibble(rownames = "Dominating Variable") %>%
  mutate(
    `Dominating Variable` = str_remove(`Dominating Variable`, "Dmnates_")
  ) %>%
  set_names(c("Dominating Variable", str_c("Dominated Variable: ", 
                                           c("ER", "AS", "SL", "WE")))) %>%
  gt(rowname_col = "Dominating Variable") %>%
  tab_header("Table S21: Negative Binomial Model Complete Dominance Designations") %>%
  sub_missing() %>% 
  tab_stubhead("Dominating Variable")
```

<!-- # ~~~ NB regs don't work with dominance_analysis() - method dispatch issue? -->
<!-- # ~~~ they have r2() method but DA doesn't recognize it -->
<!-- # nb_result %>% -->
<!-- #   dominance_analysis() -->

# Differential Exposure Modeling

This section describes the model estimation and dominance analysis of the differential exposure contaminated $SJ_{RH}$/random differential exposure and the unreported $SJ_{VH}$/correlated differential exposure contaminated DVs.

## Random Differential Exposure 

The sections below estimate models focusing on the $SJ_{RH}$/random differential exposure contaminated DV.

### Without Offset Term

The results below all estimate models that do not adjust for differential exposure with an offset term.

#### Obtain Modeling Results

The code block below estimates the random differential exposure model without an offset term and reports on the results.

```{r SJ_RH-reg-no-exp}
SJ_RH_reg_wo_off <- 
  glm(SJ_RH ~ ER + AS + SL + WE, 
      data = Data_Frame, 
      family = poisson())

SJ_RH_reg_wo_off_param <- 
  SJ_RH_reg_wo_off %>% 
  parameters() 

SJ_RH_reg_wo_off_param %>% 
  select(-df_error, -CI, -z, -p) %>%
  {bind_rows(slice_tail(., n = 4), slice_head(., n = 1))} %>%
  rename(Low = "CI_low", High = "CI_high", B = "Coefficient") %>%
  mutate(`e^B` = exp(B), 
         Parameter = str_replace(Parameter, "\\(Intercept\\)", "Intercept")) %>%
  gt(rowname_col = "Parameter") %>%
  fmt_number(columns = 2:6, decimals = 4) %>%
  tab_spanner(columns = c(Low, High), label = "95% Confidence Interval") %>%
  tab_header("Table S22: Random Differential Exposure Poisson Model Without Offset Term")
```

#### Dominance Analysis Results

The code block below implements the random differential exposure model without an offset term and reports on results.

```{r SJ_RH-DA-no-exp}
SJ_RH_wo_off_DA <-
  domir(SJ_RH ~ ER + AS + SL + WE, 
        \(fml, ...) {
          res <- 
            glm(fml, ...) 
          return(r2_kullback(res, adjust = FALSE))
        },
        data = Data_Frame, family = poisson())

SJ_RH_wo_off_DA %>% 
  pluck("General_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  left_join(SJ_RH_wo_off_DA %>% 
              pluck("Standardized") %>%
              as_tibble(rownames = "Variable"),
            by = "Variable") %>%
  set_names(c("Variable", "General Dominance", "Standardized")) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S23: Random Differential Exposure Without Offset Term General Dominance Statistics") %>%
  fmt_number(columns = 2:3, decimals = 4) %>%
  tab_source_note(str_c("Overall Deviance R-square is ", 
                        SJ_RH_reg_wo_off %>% r2_kullback(adjust = FALSE) %>% 
                          sprintf("%5.4f", .), "."))

SJ_RH_wo_off_DA %>% 
  pluck("Conditional_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  set_names(c("Variable", str_c("Subset Size: ", 1:4))) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S24: Random Differential Exposure Without Offset Term  Conditional Dominance Statistics") %>%
  fmt_number(columns = 2:5, decimals = 4)

SJ_RH_wo_off_DA %>% 
  pluck("Complete_Dominance") %>%
  as_tibble(rownames = "Dominating Variable") %>%
  mutate(
    `Dominating Variable` = str_remove(`Dominating Variable`, "Dmnates_")
  ) %>%
  set_names(c("Dominating Variable", str_c("Dominated Variable: ", 
                                           c("ER", "AS", "SL", "WE")))) %>%
  gt(rowname_col = "Dominating Variable") %>%
  tab_header("Table S25: Random Differential Exposure Without Offset Term  Complete Dominance Designations") %>%
  sub_missing() %>% 
  tab_stubhead("Dominating Variable")
```

### With Offset Term

The results below all estimate models that adjust for differential exposure with an offset term.

#### Obtain Modeling Results

The code block below estimates the random differential exposure model with an offset term and reports on the results.

```{r SJ_RH-reg-exp}
SJ_RH_reg_w_off <- 
  glm(SJ_RH ~ ER + AS + SL + WE + offset(log(RH)), 
      data = Data_Frame, 
      family = poisson())

SJ_RH_reg_w_off_param <- 
  SJ_RH_reg_w_off %>% 
  parameters() 

SJ_RH_reg_w_off_param %>% 
  select(-df_error, -CI, -z, -p) %>%
  {bind_rows(slice_tail(., n = 4), slice_head(., n = 1))} %>%
  rename(Low = "CI_low", High = "CI_high", B = "Coefficient") %>%
  mutate(`e^B` = exp(B), 
         Parameter = str_replace(Parameter, "\\(Intercept\\)", "Intercept")) %>%
  gt(rowname_col = "Parameter") %>%
  fmt_number(columns = 2:6, decimals = 4) %>%
  tab_spanner(columns = c(Low, High), label = "95% Confidence Interval") %>%
  tab_header("Table S26: Random Differential Exposure Poisson Model With Offset Term")
```

#### Dominance Analysis Results

The code block below implements the random differential exposure model with an offset term and reports on results.

```{r SJ_RH-DA-exp}
SJ_RH_w_off_DA <-
  domir(SJ_RH ~ ER + AS + SL + WE, 
        \(fml, ...) {
          res <- 
            fml %>%
            update(. ~ . + offset(log(RH))) %>%
            glm(...) 
          return(r2_kullback(res, adjust = FALSE))
        },
        data = Data_Frame, family = poisson())

SJ_RH_w_off_DA %>% 
  pluck("General_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  left_join(SJ_RH_w_off_DA %>% 
              pluck("Standardized") %>%
              as_tibble(rownames = "Variable"),
            by = "Variable") %>%
  set_names(c("Variable", "General Dominance", "Standardized")) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S27: Random Differential Exposure With Offset Term General Dominance Statistics") %>%
  fmt_number(columns = 2:3, decimals = 4) %>%
  tab_source_note(str_c("Overall Deviance R-square is ", 
                        SJ_RH_reg_w_off %>% r2_kullback(adjust = FALSE) %>% 
                          sprintf("%5.4f", .), "."))

SJ_RH_w_off_DA %>% 
  pluck("Conditional_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  set_names(c("Variable", str_c("Subset Size: ", 1:4))) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S28: Random Differential Exposure With Offset Term Conditional Dominance Statistics") %>%
  fmt_number(columns = 2:5, decimals = 4)

SJ_RH_w_off_DA %>% 
  pluck("Complete_Dominance") %>%
  as_tibble(rownames = "Dominating Variable") %>%
  mutate(
    `Dominating Variable` = str_remove(`Dominating Variable`, "Dmnates_")
  ) %>%
  set_names(c("Dominating Variable", str_c("Dominated Variable: ", 
                                           c("ER", "AS", "SL", "WE")))) %>%
  gt(rowname_col = "Dominating Variable") %>%
  tab_header("Table S29: Random Differential Exposure With Offset Term Complete Dominance Designations") %>%
  sub_missing() %>% 
  tab_stubhead("Dominating Variable")
```

### Combined Differential Exposure Model Reporting

The code block below implements Table 9 as reported in the manuscript.

```{r SJ_RH-reg-table}
SJ_RH_reg_wo_off_param %>% 
  select(Parameter, Coefficient) %>%
  mutate(`e^B` = exp(Coefficient)) %>%
  left_join(
    SJ_RH_wo_off_DA %>% 
      pluck("General_Dominance") %>% 
      as_tibble(rownames = "Parameter"),
    by = "Parameter"
  ) %>%
  left_join(
    SJ_RH_reg_w_off_param %>% 
      select(Parameter, Coefficient) %>%
      rename(Coefficient = "Coefficient") %>%
      mutate(`e^B` = exp(Coefficient)),
    by = "Parameter") %>%
  left_join(
    SJ_RH_w_off_DA %>% 
      pluck("General_Dominance") %>% 
      as_tibble(rownames = "Parameter"),
    by = "Parameter"
  ) %>% 
  {bind_rows(slice_tail(., n = 4), slice_head(., n = 1))} %>%
  mutate(Parameter = str_replace(Parameter, "\\(Intercept\\)", "Intercept")) %>%
  gt(rowname_col = "Parameter") %>%
  fmt_number(columns = 2:7, decimals = 4) %>%
  tab_header("Table 9: Poisson Modeling Results Under Random Differential Exposure") %>% 
  tab_spanner(columns = c("Coefficient.x", "e^B.x", "value.x"), label = "Without Offset") %>%
  tab_spanner(columns = c("Coefficient.y", "e^B.y", "value.y"), label = "With Offset") %>%
    cols_label("Coefficient.x" ~ "B", "e^B.x" ~ "e^B", "value.x" ~ "C",
             "Coefficient.y" ~ "B", "e^B.y" ~ "e^B", "value.y" ~ "C") %>%
  sub_missing(missing_text = "") %T>%
  print %>%
  gtsave(filename = "uncorr_exp_coeff.tex", path = "./includes/")
```

## Correlated Differential Exposure 

The sections below estimate models focusing on the $SJ_{VH}$/correlated differential exposure contaminated DV.

### Without Offset Term

The results below all estimate models that do not adjust for differential exposure with an offset term.

#### Obtain Modeling Results

The code block below estimates the correlated differential exposure model without an offset term and reports on the results.

```{r SJ_VH-reg-no-exp}
SJ_VH_reg_wo_off <- 
  glm(SJ_VH ~ ER + AS + SL + WE, 
      data = Data_Frame, 
      family = poisson())

SJ_VH_reg_wo_off_param <- 
  SJ_VH_reg_wo_off %>% 
  parameters() 

SJ_VH_reg_wo_off_param %>% 
  select(-df_error, -CI, -z, -p) %>%
  {bind_rows(slice_tail(., n = 4), slice_head(., n = 1))} %>%
  rename(Low = "CI_low", High = "CI_high", B = "Coefficient") %>%
  mutate(`e^B` = exp(B), 
         Parameter = str_replace(Parameter, "\\(Intercept\\)", "Intercept")) %>%
  gt(rowname_col = "Parameter") %>%
  fmt_number(columns = 2:6, decimals = 4) %>%
  tab_spanner(columns = c(Low, High), label = "95% Confidence Interval") %>%
  tab_header("Table S30: Correlated Differential Exposure Poisson Model Without Offset Term")
```

#### Dominance Analysis Results

The code block below implements the correlated differential exposure model without an offset term and reports on results.

```{r SJ_VH-DA-no-exp}
SJ_VH_wo_off_DA <-
  domir(SJ_VH ~ ER + AS + SL + WE, 
        \(fml, ...) {
          res <- 
            glm(fml, ...) 
          return(r2_kullback(res, adjust = FALSE))
        },
        data = Data_Frame, family = poisson())

SJ_VH_wo_off_DA %>% 
  pluck("General_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  left_join(SJ_VH_wo_off_DA %>% 
              pluck("Standardized") %>%
              as_tibble(rownames = "Variable"),
            by = "Variable") %>%
  set_names(c("Variable", "General Dominance", "Standardized")) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S31: Correlated Differential Exposure Without Offset Term General Dominance Statistics") %>%
  fmt_number(columns = 2:3, decimals = 4) %>%
  tab_source_note(str_c("Overall Deviance R-square is ", 
                        SJ_VH_reg_wo_off %>% r2_kullback(adjust = FALSE) %>% 
                          sprintf("%5.4f", .), "."))

SJ_VH_wo_off_DA %>% 
  pluck("Conditional_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  set_names(c("Variable", str_c("Subset Size: ", 1:4))) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S32: Correlated Differential Exposure Without Offset Term  Conditional Dominance Statistics") %>%
  fmt_number(columns = 2:5, decimals = 4)

SJ_VH_wo_off_DA %>% 
  pluck("Complete_Dominance") %>%
  as_tibble(rownames = "Dominating Variable") %>%
  mutate(
    `Dominating Variable` = str_remove(`Dominating Variable`, "Dmnates_")
  ) %>%
  set_names(c("Dominating Variable", str_c("Dominated Variable: ", 
                                           c("ER", "AS", "SL", "WE")))) %>%
  gt(rowname_col = "Dominating Variable") %>%
  tab_header("Table S33: Correlated Differential Exposure Without Offset Term  Complete Dominance Designations") %>%
  sub_missing() %>% 
  tab_stubhead("Dominating Variable")
```

### With Offset Term

The results below all estimate models that adjust for differential exposure with an offset term.

#### Obtain Modeling Results

The code block below estimates the correlated differential exposure model with an offset term and reports on the results.

```{r SJ_VH-reg-exp}
SJ_VH_reg_w_off <- 
  glm(SJ_VH ~ ER + AS + SL + WE + offset(log(VH)), 
      data = Data_Frame, 
      family = poisson())

SJ_VH_reg_w_off_param <- 
  SJ_VH_reg_w_off %>% 
  parameters() 

SJ_VH_reg_w_off_param %>% 
  select(-df_error, -CI, -z, -p) %>%
  {bind_rows(slice_tail(., n = 4), slice_head(., n = 1))} %>%
  rename(Low = "CI_low", High = "CI_high", B = "Coefficient") %>%
  mutate(`e^B` = exp(B), 
         Parameter = str_replace(Parameter, "\\(Intercept\\)", "Intercept")) %>%
  gt(rowname_col = "Parameter") %>%
  fmt_number(columns = 2:6, decimals = 4) %>%
  tab_spanner(columns = c(Low, High), label = "95% Confidence Interval") %>%
  tab_header("Table S34: Correlated Differential Exposure Poisson Model With Offset Term")
```

#### Dominance Analysis Results

The code block below implements the correlated differential exposure model with an offset term and reports on results.

```{r SJ_VH-DA-exp}
SJ_VH_w_off_DA <-
  domir(SJ_VH ~ ER + AS + SL + WE, 
        \(fml, ...) {
          res <- 
            fml %>%
            update(. ~ . + offset(log(VH))) %>%
            glm(...) 
          return(r2_kullback(res, adjust = FALSE))
        },
        data = Data_Frame, family = poisson())

SJ_VH_w_off_DA %>% 
  pluck("General_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  left_join(SJ_VH_w_off_DA %>% 
              pluck("Standardized") %>%
              as_tibble(rownames = "Variable"),
            by = "Variable") %>%
  set_names(c("Variable", "General Dominance", "Standardized")) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S35: Correlated Differential Exposure With Offset Term General Dominance Statistics") %>%
  fmt_number(columns = 2:3, decimals = 4) %>%
  tab_source_note(str_c("Overall Deviance R-square is ", 
                        SJ_VH_reg_w_off %>% r2_kullback(adjust = FALSE) %>% 
                          sprintf("%5.4f", .), "."))

SJ_VH_w_off_DA %>% 
  pluck("Conditional_Dominance") %>%
  as_tibble(rownames = "Variable") %>%
  set_names(c("Variable", str_c("Subset Size: ", 1:4))) %>%
  gt(rowname_col = "Variable") %>%
  tab_header("Table S36: Correlated Differential Exposure With Offset Term Conditional Dominance Statistics") %>%
  fmt_number(columns = 2:5, decimals = 4)

SJ_VH_w_off_DA %>% 
  pluck("Complete_Dominance") %>%
  as_tibble(rownames = "Dominating Variable") %>%
  mutate(
    `Dominating Variable` = str_remove(`Dominating Variable`, "Dmnates_")
  ) %>%
  set_names(c("Dominating Variable", str_c("Dominated Variable: ", 
                                           c("ER", "AS", "SL", "WE")))) %>%
  gt(rowname_col = "Dominating Variable") %>%
  tab_header("Table S37: Correlated Differential Exposure With Offset Term Complete Dominance Designations") %>%
  sub_missing() %>% 
  tab_stubhead("Dominating Variable")
```

### Combined Differential Exposure Model Reporting

The code block below implements Table 10 as reported in the manuscript.

```{r SJ_VH-reg-table}
SJ_VH_reg_wo_off_param %>% 
  select(Parameter, Coefficient) %>%
  mutate(`e^B` = exp(Coefficient)) %>%
  left_join(
    SJ_VH_wo_off_DA %>% 
      pluck("General_Dominance") %>% 
      as_tibble(rownames = "Parameter"),
    by = "Parameter"
  ) %>%
  left_join(
    SJ_VH_reg_w_off_param %>% 
      select(Parameter, Coefficient) %>%
      rename(Coefficient = "Coefficient") %>%
      mutate(`e^B` = exp(Coefficient)),
    by = "Parameter") %>%
  left_join(
    SJ_VH_w_off_DA %>% 
      pluck("General_Dominance") %>% 
      as_tibble(rownames = "Parameter"),
    by = "Parameter"
  ) %>% 
  {bind_rows(slice_tail(., n = 4), slice_head(., n = 1))} %>%
  mutate(Parameter = str_replace(Parameter, "\\(Intercept\\)", "Intercept")) %>%
  gt(rowname_col = "Parameter") %>%
  fmt_number(columns = 2:7, decimals = 4) %>%
  tab_header("Table 10: Poisson Modeling Results Under Correlated Differential Exposure") %>% 
  tab_spanner(columns = c("Coefficient.x", "e^B.x", "value.x"), label = "Without Offset") %>%
  tab_spanner(columns = c("Coefficient.y", "e^B.y", "value.y"), label = "With Offset") %>%
    cols_label("Coefficient.x" ~ "B", "e^B.x" ~ "e^B", "value.x" ~ "C",
             "Coefficient.y" ~ "B", "e^B.y" ~ "e^B", "value.y" ~ "C") %>%
  sub_missing(missing_text = "") %T>%
  print %>%
  gtsave(filename = "corr_exp_coeff.tex", path = "./includes/")
```

# Records and Reproducibility

```{r records-repro}
sessionInfo()
```

The random seed information used in this session:

    84490856
    Min: 1, Max: 99999999
    2022-08-14 14:50:02 UTC
    Random.org
